---
# The YAML header specifies several settings for the survey but is not required.
# A full list of settings can be found under _survey/settings.yml directory.

theme-settings:
  theme: default
  barposition: top
  footer-left: "Made with [surveydown](https://surveydown.org)"
  footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_option_shuffling)'

survey-settings:
  show-previous: false
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-shuffled: false
  shuffled:
    - fruit_mc
    - fruit_mc_buttons
    - fruit_mc_multiple
    - fruit_mc_multiple_buttons
    - fruit_mc_buttons_1: [1-4]
    - fruit_mc_buttons_2: [4-7]
    - fruit_mc_buttons_3: [1, 3, 7]
---

```{r}
library(surveydown)
```

--- welcome

# Template - Option Shuffling

Hi! This is a showcase of option shuffling that can be applied to multiple choice questions in `{surveydown}`.

The supported question types include:

- `mc`
- `mc_buttons`
- `mc_multiple`
- `mc_multiple_buttons`

--- education

# Usage

To define option shuffling for all questions, set `all-shuffled: true` in the `survey-settings` section of the YAML header, like this:

```yaml
survey-settings:
  ...
  all-shuffled: true
```

To specify option shuffling for selected questions only, set `shuffled` in the `survey-settings` section of the YAML header, like this:

```yaml
survey-settings:
  ...
  shuffled:
    - question_id_1
    - question_id_2
```

Option shuffling can be precisely defined to selected indices, like this:

```yaml
survey-settings:
  ...
  shuffled:
    - question_id_1: [1, 2, 4, 7]
    - question_id_2: [1-5, 8-10]
```

In the above example, `question_id_1` will have options at indices 1, 2, 4, and 7 shuffled, while `question_id_2` will have options at indices 1 to 5 and 8 to 10 shuffled. If no indices are specified, all options will be shuffled.

--- question_types

This page demonstrates option shuffling in all 4 multiple choice question types.

#### Option shuffling in `type = 'mc'`:

```{r}
sd_question(
  id     = 'fruit_mc',
  type   = 'mc',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Option shuffling in `type = 'mc_buttons'`:

```{r}
sd_question(
  id     = 'fruit_mc_buttons',
  type   = 'mc_buttons',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Option shuffling in `type = 'mc_multiple'`:

```{r}
sd_question(
  id     = 'fruit_mc_multiple',
  type   = 'mc_multiple',
  label  = "Pick all your favorite fruits from this list:",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Option shuffling in `type = 'mc_multiple_buttons'`:

```{r}
sd_question(
  id     = 'fruit_mc_multiple_buttons',
  type   = 'mc_multiple_buttons',
  label  = "Pick all your favorite fruits from this list:",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

--- indices

# Shuffling with Specified Indices

This page demonstrates option shuffling with specified indices using the `mc_buttons` question type.

#### No options shuffled:
```{r}
sd_question(
  id     = 'fruit_mc_buttons_0',
  type   = 'mc_buttons',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```


#### Options 1-4 shuffled:
```{r}
sd_question(
  id     = 'fruit_mc_buttons_1',
  type   = 'mc_buttons',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Options 4-7 shuffled:
```{r}
sd_question(
  id     = 'fruit_mc_buttons_2',
  type   = 'mc_buttons',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

#### Options 1, 3, 7 shuffled:
```{r}
sd_question(
  id     = 'fruit_mc_buttons_3',
  type   = 'mc_buttons',
  label  = "Which fruit do you prefer most from this list?",
  option = c(
    "Apple"      = "apple",
    "Banana"     = "banana",
    "Pear"       = "pear",
    "Strawberry" = "strawberry",
    "Grape"      = "grape",
    "Mango"      = "mango",
    "Watermelon" = "watermelon"
  )
)
```

--- end

## Thanks for taking our survey!

```{r}
sd_close()
```
